\begin{abstract}
Welcome to the practicals for EEE3096S. These instruction are applicable to all practicals so please take note! It is critical to do the pre-practical/tutorial work. 
Tutors will not help you with questions with answers that would have been known had you done the pre-practical work. 
The UCT EE Wiki (\href{wiki.ee.uct.ac.za}{wiki.ee.uct.ac.za}) is a very useful point to find any additional learning resources you might need. Use the search functionality on the top right of the page.

\subsection*{Practical Instructions}
\begin{itemize}
    \item \textbf{Naming}\\
    All files submitted to Vula need to be in the format. Marks will be deducted if not.
    \begin{lstlisting}[gobble=4]
    pracnum_studnum1_studnum2.fileformat
    \end{lstlisting}
    \item \textbf{Submission}
    \begin{itemize}
        \item Work packages consist of a tutorial and a practical. Be sure you submit to the correct submission on Vula!
        \item All text assignments must be submitted as pdf, and pdf only.
        \item Code within PDFs should not be as a screenshot, but as text. 
        \item Where appropriate, each pdf should contain a link to your GitHub repository.
    \end{itemize}
    \item \textbf{Groups}\\
    All practicals are to be completed in groups of 2. If a group of 2 can't be formed, permission will be needed to form a group of 3.
    \item \textbf{Bonus Marks}\\
    Occasionally, practicals will have ``bonus marks". If you do get bonus marks, the total marks for your prac cannot go over 100\%.
    \item \textbf{Mark Deductions}\\
    Occasionally, marks will be deducted from practicals. These will be conveyed to you in the practical, but many will be consistent across practicals, such as incorrectly names submissions or including code as a screenshot instead of formatted text.
    \item \textbf{Late Penalties}\\
    Late penalties will work as 10\% deduction per day, up to a maximum of 30\%. After this, you will receive 0\% and have the submission marked as incomplete.
    
\end{itemize}

\end{abstract}

